DraftOne

### 2016-06-06 DraftOne.Rmd
Adding calc_t to package

First, we need to generate the explanatory exposure variable.  Here is a function for binary exposure in which the probability varies by season.  Later we will add a function for continuous exposure which varies by season (~Normal(mu, sigma)).

@@

Now a function to calculate the trend variable. Choices for trend are cvd, cos1, cos2, cos3, linear, curvilinear, cos1linear.

```{r}
calc_t <- function(n, trend){
  day <- c(1:n)
  if (trend == "cos1"){
    seasont <- 1+.6*cos(2*pi*(day/365))
  }
  if (trend == "cos2"){
    seasont <- 1+.6*cos(2*pi*(day/365)) + ifelse(day<639 & day>274, .4*cos(2*(pi*(day/365))), 0)
  }
  if (trend == "cos3"){
    seasont <- 1+.75^(day/365)*.6*cos(2*pi*(day/365))
  }
  if (trend == "linear"){
    seasont <- 1+ (day/n)
  }
  if (trend == "curvilinear"){
    seasont <- 1+day*(2/n)+day^2*(-1/n^2)
  }
  if (trend == "cos1linear"){
    seasont <- (1+(day/n)) *(1+.6*cos(2*pi*(day/365)))
  }
  if (trend == "cvd"){ #Figure this out later.
  } #else{
    #stop("Specify a trend variable from cos1, cos2, cos3, linear, curvilinear, cos1linear, or cvd."
    #)}
  return(seasont)
}
```

>>>>

A function to calculate the trend variable. Choices for trend are cvd, cos1, cos2, cos3, linear, curvilinear, cos1linear.

```{r}
calc_t 
```

We need to generate the explanatory exposure variable.  Here are functions for binary and continuous exposure which varies by season.

@@
